PANCHANGE_variable_creation

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
Added keyworker status to employment variable

### Ethnicity
```{r freq table ethnicity}
dat %>%
  freq(Ethnicity_collapsed) 
```
### Gender
```{r freq table gender}
dat %>%
  freq(Gender_collapsed) 
```
### age categorical
```{r freq table age collapsed}
dat %>%
  freq(age_category_collapsed) 
```

>>>>

### Ethnicity
```{r freq table ethnicity}
dat %>%
  freq(Ethnicity_collapsed) 
```
### Gender
```{r freq table gender}
dat %>%
  freq(Gender_collapsed) 
```
### age categorical
```{r freq table age collapsed}
dat %>%
  freq(age_category_collapsed) 
```
### Employment

```{r freq table employment collapsed}
dat %>%
  freq(employment_prior_covid) 
```

### 2020-12-16 PANCHANGE_variable_creation.Rmd
Added keyworker status to employment variable

## Read in data
```{r read in data}
dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat)
colnames(dat)
```

@@

>>>>

## Read in data
```{r read in data}
dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat)
```

@@

## Employment
Adjust so employed category is keyworker vs non keyworker

```{r adjust employment prior covid category}

dat <- 
  dat %>%
  mutate(employment_prior_covid_2 =  
           case_when(dat$employment_prior_covid == "Employed" & key_worker == "Key worker" ~ "Key worker",
                     dat$employment_prior_covid == "Employed" & key_worker == "No key worker" ~ "Employed",
                    dat$employment_prior_covid == "Unemployed" ~ "Unemployed",
                     dat$employment_prior_covid == "Student" ~ "Student",
                    dat$employment_prior_covid == "Retired" ~ "Retired"))

dat$employment_prior_covid <- dat$employment_prior_covid_2
